---
title: "HotOnesSauces"
author: "Benjamin Robbins"
date: "2023-11-06"
output: html_document
---

ALL COMMENTS START WITH #DMC#

# DMC# I added "readr" library
```{r}
library(tidyverse)
library(lubridate)
library(readr)
library(skimr) 
library(visdat)
library(plotly)

library(corrplot)
```

## R Markdown

```{r}
data_dir <- 'data'
target_file <- file.path(data_dir, 'sauces.zip')

if (dir.exists(data_dir)) {
  dir.create(data_dir)
}

if (!file.exists(target_file)) {
  download.file('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-08-08/sauces.csv',
                target_file)
}
```

# Error because library readr was missing. I added it for reproduce the code.
```{r}
dataf <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-08-08/sauces.csv')
```

```{r}
skim(dataf)
```

```{r}
sauces <- tryCatch(
  read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-08-08/sauces.csv'),
  error = function(e) {
    cat("Error:", conditionMessage(e), "\n")
    sauces <- NULL
  }
)
if (!is.null(sauces)) {
  head(sauces)
} else {
  cat("Failed to load the 'sauces' dataset.\n")
}
head(sauces)
```

```{r}
summary(sauces)
```

```{r}
str(sauces)
```

```{r}
summary(sauces$sauce_number, sauce_name, scoville)
```

```{r}
summary(select(sauces, sauce_number, sauce_name, scoville))
```
# DMC# I suggest to explain why you create this value. 
```{r}
scoville_column <- "scoville"
```

# DMC# Same, brief comment about what is this chunk of code. 
```{r}
sauces$numeric_sauce_name <- as.numeric(factor(sauces$sauce_name))
unique_values <- unique(sauces$numeric_sauce_name)
print(unique_values)
```

```{r}
if (scoville_column %in% names(sauces)) {
  print("Column 'scoville' found in the dataset.")
} else {
  print("Column 'scoville' not found in the dataset.")
}
```

# DMC# Rename variables for more clarity
```{r}
correlation_matrix <- cor(select(sauces, numeric_sauce_name, scoville))
corrplot(correlation_matrix, method = "color")
```

```{r}
correlation_matrix <- cor(sauces[, c("numeric_sauce_name", "sauce_number")])
print(correlation_matrix)
```

# DMC# Brief comment, I don't know what you want to show, I am not familiar with this "plot"/cross tab
```{r}
cross_tab <- table(sauces$season, sauces$sauce_name)
print(cross_tab)
mosaicplot(cross_tab, color = TRUE)
```
# DMC# Brief comment
```{r}
pairs(sauces[c("season", "sauce_number", "numeric_sauce_name")])
```

## Including Plots

# DMC# Rename variables (delete "_"), it's just a small detail, it's looks good anyways. Do it for the rest of the plots. 
```{r}
ggplot(sauces, aes(x = sauce_number)) +
  geom_histogram(binwidth = 5, fill = "blue", color = "black") +
  labs(title = "Histogram of Sauce Number")
```

```{r}
ggplot(sauces, aes(x = sauce_name)) +
  geom_bar(fill = "green") +
  labs(title = "Bar Plot of Sauce Name")
```

```{r}
ggplot(sauces, aes(x = scoville)) +
  geom_bar(fill = "orange") +
  labs(title = "Scoville Ratings Distribution", x = "Scoville Rating") +
  theme_minimal()
```

```{r}
ggplot(sauces, aes(x = sauce_name, y = scoville)) +
  geom_boxplot(fill = "purple") +
  labs(title = "Box Plot of Scoville by Sauce Name")
```

```{r}
ggplot(sauces, aes(x = sauce_name, y = sauce_number)) +
  geom_point(color = "red") +
  labs(title = "Scatterplot of Sauce Name vs. Sauce Number")
```
