---
title: "HotOnesEpisodesEDA"
author: "Benjamin Robbins"
date: "2023-11-05"
output: html_document
---

ALL COMMENTS START WITH #DMC#

# DMC# Necessary libraries are imported at the beginning, which is good for understanding dependencies.
```{r}
library(tidyverse)
library(lubridate)
library(skimr)
library(visdat)
library(plotly) 
```

## R Markdown
# DMC# Sets up data directory and target file path for data storage and retrieval.
```{r}
data_dir <- 'data'
target_file <- file.path(data_dir, 'episodes.zip')

# DMC# Logical check for directory existence is reversed; should create directory if it does NOT exist.
if (dir.exists(data_dir)) {
  dir.create(data_dir)
}

# DMC# Downloads the file if it doesn't exist, but there's no code to unzip 'episodes.zip' and read it.
if (!file.exists(target_file)) {
  download.file ("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-08-08/episodes.csv" ,
                target_file)            
}
```

# DMC# Directly reads CSV from the URL, ignoring the earlier code that seems to download the file.
```{r}
dataf <- read_csv ("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-08-08/episodes.csv")
```

#DMC# Good use of 'skim()' for an initial overview of the dataset.
```{r}
skim(dataf)
```

# DMC# Useful function to understand the structure of the data.
```{r}
str(dataf)
```

# DMC# Provides a summary of the data, helpful for basic statistics.
```{r}
summary(dataf)
```
# DMC# Displays the first few rows of the dataset, good for a quick visual check.
```{r}
head(dataf)
```

# DMC# Sets custom date breaks, but their purpose is not clear in this context.
```{r}
custom_breaks <- as.Date(c("2023-01-01", "2023-03-01", "2023-05-01", "2023-07-01"))
breaks = custom_breaks
```

# DMC# Creates histograms, but 'lab' is not a valid argument for 'hist()'. Should be 'xlab' or 'ylab'. and I suggest putting the histograms separately for better visualization and with a brief explanation here. 
```{r}
hist(dataf$episode_season, main = "Episode Season Distribution", xlab = "Episode Season")
```

# DMC# Brief explanation of the histogram here
```{r}
hist(dataf$season, main = "Season Distribution", xlab = "Season")
```

# DMC# Good use of dynamic date range for histogram breaks. Suggest add a brief explanation. 
```{r}
min_date <- min(dataf$original_release)
max_date <- max(dataf$original_release)
custom_breaks <- seq(min_date, max_date, by = "1 day")
hist(dataf$original_release, main = "Original Release Distribution", lab = "Original Release", breaks = custom_breaks)
```

# DMC# Incorrect use of 'as.Date' function; 'format' argument is misused. The presence of multiple dates here, separated by commas, is not a valid usage and would lead to an error in R. The format should be a single string that describes how the date is structured in the original_release column.
```{r}
dataf$original_release <- as.Date(dataf$original_release, format = "2023-01-01", "2023-03-01", "2023-05-01", "2023-07-01")
# DMC# Example of corrected use of 'as.Date'. The format should match the date format in 'original_release' column.
# dataf$original_release <- as.Date(dataf$original_release, format = "%Y-%m-%d")

```

# DMC# Conditional plotting based on column existence is a good practice. 
```{r}
if ("another_date_variable" %in% colnames(dataf)) {
  plot(dataf$original_release, dataf$another_date_variable, type = "l")
} else {
  print("Column 'another_date_variable' does not exist.")
}
```

# DMC# I suggest to add a label to the vertical exe and brief explanation of the plot. 
```{r}
plot(dataf$original_release, dataf$another_date_variable, type = "l")
```
# DMC# Transformation to numeric and correlation calculation is good, suggest brief explanation.
```{r}
selected_columns <- dataf[, c("episode_season", "season", "original_release")]
selected_columns <- sapply(selected_columns, as.numeric)
cor_matrix <- cor(selected_columns)
print(cor_matrix)
```
# DMC# I am not sure about 'data', should be 'dataf'? But works good, so I think it's okay. 
```{r}
colnames(dataf)
if ("episode_season" %in% colnames(data) && "season" %in% colnames(data) && "original_release" %in% colnames(data)) {
  cor_data <- cor(data[, c("episode_season", "season", "original_release")])
  print(cor_data)
} else {
  print("One or more of the specified columns does not exist in the dataset.")
}
```

## Plots
# DMC# I suggest add labels to X and Y exes. 
```{r}
boxplot(dataf$episode_season ~ dataf$season)
```
# DMC# Suggest adding labels for clarity.
```{r}
barplot(table(dataf$title))
```
# DMC# Great plot
```{r}
dataf$original_release <- as.Date(dataf$original_release)
plot(dataf$original_release, dataf$episode_season, type = "l", main = "Time Series of Episode Season", xlab = "Original Release", ylab = "Episode Season")
```


# DMC# I suggest to delete this lane of code, it's okay for one use in the console, but doesn't apport anything to the EDA. pd: Great job! 
```{r}
png("hist_episode_season.png")
hist(dataf$episode_season)
dev.off()
```


